%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
% !TeX spellcheck = en
\documentclass{resume} % Use the custom resume.cls style
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=cyan,      
    urlcolor=cyan,
}
\usepackage{mathpazo}

\urlstyle{same}

\usepackage[left=0.75in,top=0.52in,right=0.75in,bottom=0.52in]{geometry} % Document margins
%\usepackage[colorlinks=black, linkcolor=black, urlcolor=cyan]{hyperref}
\usepackage{marvosym}
\usepackage{graphicx}

\name{Siddhi Jha}
\address{\href{mailto:siddhijha023@gmail.com}{siddhijha023@gmail.com} \\
         \href{https://www.linkedin.com/in/siddhi-jha/}{in/siddhi\_jha}\ \\
         \href{https://github.com/siddhi523}{github.com/siddhi} \\
         %\href{https://github.com/championshuttler/}{github.com/championshuttler} \\
         +91-9971584787}

\begin{document}

%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Summary}
 % \begin{rSummarySection}
  %{
   % \item Experience with java, web development, machine learning and problem solving.
    %\item Java, Python3, Django, MySQL, Praw, Machine Learning, Git.
  %}
  %\end{rSummarySection}
%\end{rSection}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
  \begin{rEducationSection}{Maharaja Surajmal Institute of Technology}
                           {New Delhi, IN}
                           {Bachelor of Technology}
                           {Aug '17 -- Present}
{
  \item Major: Information Technology
  \item Key Courses taken: Data Structures and algorithms, Applied Mathematics, Theory of Computation, Operating System, Data Communication and networks.
  \item CGPA -- 8.85
   }                                         
  \end{rEducationSection}
  
  \begin{rEducationSection}{Webtek Labs Private Limited}
                            {New Delhi, IN}
                           {Java Industrial Training}
                           {May '18 -- July '18}
 {
  \item Curriculum: oops principles, collections, logic building.
  \item Learned java from basic to intermediate everything with the help of projects made from scratch.
   }                                         
  \end{rEducationSection}
  
\end{rSection}

%----------------------------------------------------------------------------------------
% SKILL SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}
  \begin{rSkillSection}
    \item \textbf {Technical Skills} -- Java, Python3, Git, Django, JSP, HTML5, CSS3
    \vspace{3mm}
    \item \textbf {Soft Skills} --  Bilingual Communicator (English, Hindi), Public Speaker
    \vspace{3mm}
  \end{rSkillSection}
\end{rSection}

%----------------------------------------------------------------------------------------
% WORK SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}
  \begin{rWorkSection}{Maharaja Surajmal Institute of Technology}
                           {New Delhi, IN}
                           {ENVA Event Head}
                           {Jan -- Feb '19}
  {
    \item Organised the annual cultural fest of Prakriti, MSIT - ENVA '19
    \item Helped promoting the event and raise funds for the same
    \item Received excellent feedback from professors
  }
  \end{rWorkSection}


  \begin{rWorkSection}{TeacherOn}
                     {New Delhi, IN}
                     {High School tutor}
                     {May -- Nov '19}
  {
    \item Taught chemistry to a high school student.
    \item Received excellent feedback from student and her family.
    %\item Rewrote referral invites system, with shareable url and email invites support to expand reach of platform.
  }
  \end{rWorkSection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}
  \begin{rProjectSection}
    \item \textbf {Reddit Flair Detector} -- Website to predict flair of a Reddit post. It takes a Reddit post URL as input and display it's predicted flair. Attributes used : title, body, comments. Written in \href{https://github.com/siddhi523/reddit_flair_detector_}{Python}
    \vspace{3mm}
    \item \textbf {Online Quiz Game} --  Portal for question answer sessions like a survey. This platform could be used by teachers to register and create quizzes and students can answer them later. Written in \href{https://github.com/siddhi523/Online_Quiz_Game}{Java}
    \vspace{3mm}
    \item \textbf {Employee Management System} -- A management system where an employer can Create, Read, Update and Delete data of it's employees efficiently.\href{https://www.semanticscholar.org/paper/Empirical-Analysis-of-Cervical-and-Breast-Cancer-Kaur-Pruthi/28fd7fd826460167a685b29cf3f56cfe83da1cb6}{Project's repository}
    \vspace{3mm}
    \item My other projects can be \href{https://github.com/siddhi523?tab=repositories}{found here}
  \end{rProjectSection}

  \begin{rBlurbSection}
    \item {\em Open-source contributions:}
      I am an active OSS contributor. My \href{https://github.com/pulls}{\textbf{PR's}}.
  \end{rBlurbSection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	Talks Section
%----------------------------------------------------------------------------------------

\begin{rSection}{Leadership and Awards}
  \begin{rProjectSection}
    \item \textbf {Merit Scholarship Holder} -- Session 2017-2018 and 2018-2019.
  \end{rProjectSection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	VOLUNTEER EXPERIENCE
%----------------------------------------------------------------------------------------

%\begin{rSection}{Volunteer Experience}
 % \begin{tabular}{rll}
%2019	    & {\href{http://www.msit.in/media/2019/03/20/report-on-enva.pdf}{ENVA}}  & Event Head of the annual cultural fest of Prakriti,MSIT\\
%\end{tabular}
%\end{rSection}



\end{document}
